On $K_2$-analogue of Serre problem for $\SL_4$

### 2018-08-28 paper.tex
Minor

Now suppose  $1 \leq d \leq m+1$. Clearly \eqref{lem:bmp1} and \eqref{eq:defmpn} (in the case $d\leq m$) or~\cref{lem:bmp1} (in the case $d=m+1$) imply that
\begin{equation} \label{eq:verify-bmp1'} 
[S_\alpha(\xi), x_{\alpha'}(\eta)] = S_{\alpha+\alpha'}(N_{\alpha,\alpha'}\xi \eta),\ \xi \in B_d, \eta \in B_{m+1-d}.
\end{equation}

\begin{lemma}
 For $\xi \in B_d$, $d\leq m+1$, $\eta \in B_{m+1}$ and $\alpha, \alpha' \in \Phi$ such that $\alpha + \alpha'\not\in\Phi\cup\{0\}$
 the following relation holds in $G_m$:
  \begin{equation} \label{eq:verify-bmp2} [S_\alpha(\xi), S_{\alpha'}(\eta)] = 1. \end{equation}
\end{lemma}
\begin{proof}
Write $\eta = bt^{m+1}$ for some $b\in A$.
\begin{enumerate}
\item \label{case:1} First consider the case $d \leq 0$. There are two further subcases.
 \begin{enumerate}
  \item \label{case:1a} Case $\alpha \not \perp \alpha'$. 
  Without loss of generality we may assume that $\alpha' = \alpha + \beta$
  for some $\rA_3$-triple $(\alpha, \beta, \gamma)$.
  Using~\eqref{eq:H1iii} and~\eqref{eq:bm} we obtain
   \begin{multline} \nonumber
   [S_\alpha(\xi), S_{\alpha+\beta}(bt^{m+1})] = [x_\alpha(\xi), [x_{\alpha+\beta+\gamma}(b't^m), x_{-\gamma}(t)]] = \\   
  = [[x_\alpha(\xi), x_{\alpha+\beta+\gamma}(b't^m)], {}^{x_{\alpha+\beta+\gamma}(b't^m)}\!x_{-\gamma}(t)] = 1 \text{ for some $b'\in A$ }.
  \end{multline}
  %What this really proves: $b_{m}(\alpha, |\xi|, -\gamma, 1)$ and $b_m(\alpha, |\xi|, \alpha+\beta+\gamma, m)$ implies $b_{m+1}(\alpha, |\xi|, \alpha+\beta, m+1 )$.
  \item Case $\alpha \perp \alpha'$. 
  As before, we set $\alpha' = \gamma$ and use~\eqref{eq:H1iii},\eqref{eq:bm} and~\eqref{eq:cm}:
  \begin{multline} \nonumber
   [x_\alpha(\xi), S_{\gamma}(bt^{m+1})] = [x_\alpha(\xi), [x_{\beta+\gamma}(b't^m), x_{-\beta}(t)]] = \\   
  = [[x_\alpha(\xi), x_{\beta+\gamma}(b't^m)], {}^{x_{\beta+\gamma}(b't^m)}\!x_{-\beta}(t)] = {}^{x_{\beta+\gamma}(b't^m)}\![x_{\alpha+\beta+\gamma}(b't^m\xi), x_{-\beta}(t)] = 1.
  \end{multline}
 \end{enumerate}

>>>>

Now suppose  $0 \leq d \leq m+1$. Clearly \eqref{lem:bmp1} and \eqref{eq:defmpn} (in the case $1\leq d\leq m$) or~\cref{lem:bmp1} (in the case $d=0,m+1$) imply that
\begin{equation} \label{eq:verify-bmp1'} 
[S_\alpha(\xi), x_{\alpha'}(\eta)] = S_{\alpha+\alpha'}(N_{\alpha,\alpha'}\xi \eta),\ \xi \in B_d, \eta \in B_{m+1-d}.
\end{equation}

\begin{lemma}
 For $\xi \in B_d$, $d\leq m+1$, $\eta \in B_{m+1}$ and $\alpha, \alpha' \in \Phi$ such that $\alpha + \alpha'\not\in\Phi\cup\{0\}$
 the following relation holds in $G_m$:
  \begin{equation} \label{eq:verify-bmp2} [S_\alpha(\xi), S_{\alpha'}(\eta)] = 1. \end{equation}
\end{lemma}
\begin{proof}
Write $\eta = bt^{m+1}$ for some $b\in A$.
\begin{enumerate}
\item \label{case:1} First consider the case $d \leq 0$. There are two further subcases.
 \begin{enumerate}
  \item \label{case:1a} Case $\alpha \not \perp \alpha'$. 
  Without loss of generality we may assume that $\alpha' = \alpha + \beta$
  for some $\rA_3$-triple $(\alpha, \beta, \gamma)$.
  Using~\eqref{eq:H1iii} and~\eqref{eq:bm} we obtain
   \begin{multline} \nonumber
   [S_\alpha(\xi), S_{\alpha+\beta}(bt^{m+1})] = [x_\alpha(\xi), [x_{\alpha+\beta+\gamma}(b't^m), x_{-\gamma}(t)]] = \\   
  = [[x_\alpha(\xi), x_{\alpha+\beta+\gamma}(b't^m)], {}^{x_{\alpha+\beta+\gamma}(b't^m)}\!x_{-\gamma}(t)] = 1 \text{ for some $b'\in A$ }.
  \end{multline}
  What this really proves: $PERP(d, 1)$ and $NONPERP(d, m)$ imply $NONPERP(d, m+1)$.
  \item Case $\alpha \perp \alpha'$. 
  As before, we set $\alpha' = \gamma$ and use~\eqref{eq:H1iii},\eqref{eq:bm} and~\eqref{eq:cm}:
  \begin{multline} \nonumber
   [S_\alpha(\xi), S_{\gamma}(bt^{m+1})] = [S_\alpha(\xi), [x_{\beta+\gamma}(b't^m), x_{-\beta}(t)]] = \\   
  = [[S_\alpha(\xi), x_{\beta+\gamma}(b't^m)], {}^{x_{\beta+\gamma}(b't^m)}\!x_{-\beta}(t)] = {}^{x_{\beta+\gamma}(b't^m)}\![x_{\alpha+\beta+\gamma}(b't^m\xi), x_{-\beta}(t)] = 1.
  \end{multline}
 \end{enumerate}
